Refactoring the `nls()` function in R

### 2022-07-24 RefactoringNLS/RefactoringNLS.Rmd
More corrections

@@

@@

One obvious case is that nonlinear modeling tools are a superset of linear ones.
Yet the explicit model `y ~ a * x + b` does not work with the linear modeling 
function `lm()`, which requires this model to be specified as `y ~ x`.

Within `nls()`, consider the 
following FOUR different calling sequences for the same problem, though an intuitive choice,
labelled fm2a, will not work. In this failed
attempt, putting the `Asym` parameter in the model causes the `plinear` algorithm
to try to add another term to the model. We believe this is unfortunate, and would
like to see a consistent syntax. At the time of writing, we do
not foresee a resolution for this issue. In the example, we have NOT evaluated
the commands to save space.

>>>>

<!-- ?? nlme::gnls() -- should we note it? -->

@@

SHORT EXAMPLE??

```{r nlswtx, echo=TRUE}
weed <- c(5.308, 7.24, 9.638, 12.866, 17.069, 23.192, 31.443,
          38.558, 50.156, 62.948, 75.995, 91.972)
tt <- 1:12
weeddf <- data.frame(tt, weed)
wts <- 0.5^tt # simple weights
frmlogis <- weed ~ Asym/(1 + exp((xmid - tt)/scal))
Asym<-1; xmid<-1; scal<-1
nowt<-nls(weed ~ SSlogis(tt, Asym, xmid, scal))
nowt
nowt$m$resid()
inpar<-getInitial(weed ~ SSlogis(tt, Asym, xmid, scal), data=weeddf)
print(inpar)
library(nlsr2)
nowtx<-nlxb(frmlogis, start=c(Asym=1, xmid=1, scal=1), trace=TRUE)
nowtx
# nowtSSx0<-nlxb(weed ~ SSlogis(tt, Asym=1, xmid=1, scal=1), start=c(Asym=1, xmid=1, scal=1), trace=TRUE)
# nowtSsx0
# nowtSSx<-nlxb(weed ~ SSlogis(tt, Asym=1, xmid=1, scal=1), start=c(Asym=100, xmid=2, scal=1), trace=TRUE, 
#               control=list(japprox="jand"))
# nowtSSx
nowtxi<-nlxb(frmlogis, start=inpar, trace=TRUE)
nowtxi
usewt <- nls(weed ~ SSlogis(tt, Asym, xmid, scal), weights=wts)
usewt
usewt$m$resid()
nmod <- nlsModel(frmlogis, data=weeddf, start=c(Asym=1, xmid=1, scal=1), wts=wts)
usewtx<-nlxb(frmlogis,  start=c(Asym=1, xmid=1, scal=1), weights=wts, trace=TRUE)
usewtx
# NOTE jafwd and jaback fail!
usewtxn<-nlxb(frmlogis,  start=c(Asym=1, xmid=1, scal=1), weights=wts, trace=TRUE, control=list(japprox="jacentral"))
usewtxn
usewtxi<-nlxb(frmlogis, start=inpar, weights=wts, trace=TRUE)
usewtxi
# usewtx$resid
```

@@

The nonlinear modeling model specifications are, of course, a development of linear ones.
Unfortunately, the explicit model `y ~ a * x + b` does not work with the linear modeling 
function `lm()`, which requires this model to be specified as `y ~ x`.

Within `nls()`, consider the following FOUR different specifications for the same problem, plus 
an intuitive choice, labelled fm2a, that does not work. In this failed
attempt, putting the `Asym` parameter in the model causes the `plinear` algorithm
to try to add another term to the model. We believe this is unfortunate, and would
like to see a consistent syntax. At the time of writing, we do
not foresee a resolution for this issue. In the example, we have NOT evaluated
the commands to save space.
